An Introduction to Rocker: Docker Containers for R

### 2015-02-01 manuscript.Rmd
header fixes

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Santa Cruz
    address:
    - line 1
    - line 2
    email:  cboettig@ropensci.org
  - name: Dirk Eddlebuettel
    affiliation: Debian, ...
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
  An abstract of less than 150 words.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

>>>>

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Santa Cruz
    address:
    - line 1
    - line 2
    email:  cboettig@ropensci.org
  - name: Dirk Eddelbuettel
    affiliation: Debian and R Projects
    address:
    - line 1
    - line 2
    email:  edd@debian.org
abstract: >
  An abstract of less than 150 words.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---
